Towards Practical First-Order Model Counting

### 2024-08-09 doc/paper/plot.tex
First (second?) draft of the 'experiments' section

% Created by tikzDevice version 0.12.6 on 2024-07-30 13:11:15
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 48.13, 57.56) --
	( 48.13,198.75);

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 85.60, 57.56) --
	( 85.60,198.75);

\path[draw=drawColor,line width= 0.2pt,line join=round] (123.07, 57.56) --
	(123.07,198.75);

\path[draw=drawColor,line width= 0.2pt,line join=round] (160.53, 57.56) --
	(160.53,198.75);

@@

\path[draw=drawColor,line width= 0.5pt,line join=round] ( 66.87, 57.56) --
	( 66.87,198.75);

\path[draw=drawColor,line width= 0.5pt,line join=round] (104.33, 57.56) --
	(104.33,198.75);

\path[draw=drawColor,line width= 0.5pt,line join=round] (141.80, 57.56) --
	(141.80,198.75);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.10,106.36) --
	( 45.46,106.36) --
	( 50.81,106.36) --
	( 56.16,106.36) --
	( 61.51,106.36) --
	( 66.87,106.36) --
	( 72.22,106.37) --
	( 77.57,106.38) --
	( 82.92,106.42) --
	( 88.28,106.58) --
	( 93.63,107.23) --
	( 98.98,109.99) --
	(104.33,117.90);
\definecolor{drawColor}{RGB}{117,112,179}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 45.46,123.48) --
	( 50.81,112.22) --
	( 56.16,112.22) --
	( 61.51,112.42) --
	( 66.87,119.02) --
	( 72.22,162.96);
\definecolor{fillColor}{RGB}{27,158,119}

@@

\path[fill=fillColor] ( 45.46,106.36) circle (  1.96);

\path[fill=fillColor] ( 50.81,106.36) circle (  1.96);

\path[fill=fillColor] ( 56.16,106.36) circle (  1.96);

\path[fill=fillColor] ( 61.51,106.36) circle (  1.96);

\path[fill=fillColor] ( 66.87,106.36) circle (  1.96);

\path[fill=fillColor] ( 72.22,106.37) circle (  1.96);

\path[fill=fillColor] ( 77.57,106.38) circle (  1.96);

\path[fill=fillColor] ( 82.92,106.42) circle (  1.96);

\path[fill=fillColor] ( 88.28,106.58) circle (  1.96);

\path[fill=fillColor] ( 93.63,107.23) circle (  1.96);

\path[fill=fillColor] ( 98.98,109.99) circle (  1.96);

\path[fill=fillColor] (104.33,117.90) circle (  1.96);
\definecolor{fillColor}{RGB}{117,112,179}

\path[fill=fillColor] ( 43.49,121.52) --
	( 47.42,121.52) --
	( 47.42,125.44) --
	( 43.49,125.44) --
	cycle;

\path[fill=fillColor] ( 48.85,110.26) --
	( 52.77,110.26) --
	( 52.77,114.18) --
	( 48.85,114.18) --
	cycle;

\path[fill=fillColor] ( 54.20,110.26) --
	( 58.12,110.26) --
	( 58.12,114.18) --
	( 54.20,114.18) --
	cycle;

\path[fill=fillColor] ( 59.55,110.46) --
	( 63.47,110.46) --
	( 63.47,114.38) --
	( 59.55,114.38) --
	cycle;

\path[fill=fillColor] ( 64.90,117.06) --
	( 68.83,117.06) --
	( 68.83,120.99) --
	( 64.90,120.99) --
	cycle;

\path[fill=fillColor] ( 70.26,161.00) --
	( 74.18,161.00) --
	( 74.18,164.92) --
	( 70.26,164.92) --
	cycle;
\definecolor{drawColor}{gray}{0.70}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 34.75, 57.56) -- ( 34.75, 63.25);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 45.46, 57.56) -- ( 45.46, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 50.81, 57.56) -- ( 50.81, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 56.16, 57.56) -- ( 56.16, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 61.51, 57.56) -- ( 61.51, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 66.87, 57.56) -- ( 66.87, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 72.22, 57.56) -- ( 72.22, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 77.57, 57.56) -- ( 77.57, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 82.92, 57.56) -- ( 82.92, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 88.28, 57.56) -- ( 88.28, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 93.63, 57.56) -- ( 93.63, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 98.98, 57.56) -- ( 98.98, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (104.33, 57.56) -- (104.33, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (109.69, 57.56) -- (109.69, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (115.04, 57.56) -- (115.04, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (120.39, 57.56) -- (120.39, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (125.74, 57.56) -- (125.74, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (131.10, 57.56) -- (131.10, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (136.45, 57.56) -- (136.45, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (141.80, 57.56) -- (141.80, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (147.15, 57.56) -- (147.15, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (152.51, 57.56) -- (152.51, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (157.86, 57.56) -- (157.86, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (163.21, 57.56) -- (163.21, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (168.56, 57.56) -- (168.56, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (173.92, 57.56) -- (173.92, 63.25);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (184.62, 57.56) -- (184.62, 63.25);

@@

\path[draw=drawColor,line width= 0.2pt,line join=round] (205.71, 57.56) --
	(205.71,198.75);

\path[draw=drawColor,line width= 0.2pt,line join=round] (243.18, 57.56) --
	(243.18,198.75);

\path[draw=drawColor,line width= 0.2pt,line join=round] (280.65, 57.56) --
	(280.65,198.75);

\path[draw=drawColor,line width= 0.2pt,line join=round] (318.12, 57.56) --
	(318.12,198.75);

@@

\path[draw=drawColor,line width= 0.5pt,line join=round] (224.45, 57.56) --
	(224.45,198.75);

\path[draw=drawColor,line width= 0.5pt,line join=round] (261.91, 57.56) --
	(261.91,198.75);

\path[draw=drawColor,line width= 0.5pt,line join=round] (299.38, 57.56) --
	(299.38,198.75);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (197.68, 87.62) --
	(203.04, 87.62) --
	(208.39, 87.61) --
	(213.74, 87.61) --
	(219.09, 87.61) --
	(224.45, 87.61) --
	(229.80, 87.61) --
	(235.15, 87.62) --
	(240.50, 87.69) --
	(245.86, 88.58) --
	(251.21, 97.29) --
	(256.56,123.32) --
	(261.91,157.55) --
	(267.27,192.33);
\definecolor{drawColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (197.68, 87.37) --
	(203.04, 87.37) --
	(208.39, 87.36) --
	(213.74, 87.36) --
	(219.09, 87.36) --
	(224.45, 87.36) --
	(229.80, 87.36) --
	(235.15, 87.37) --
	(240.50, 87.44) --
	(245.86, 88.34) --
	(251.21, 97.16) --
	(256.56,123.35) --
	(261.91,157.54) --
	(267.27,192.33);
\definecolor{drawColor}{RGB}{117,112,179}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (203.04,113.24) --
	(208.39,111.85) --
	(213.74,111.59) --
	(219.09,111.66) --
	(224.45,112.12) --
	(229.80,112.27) --
	(235.15,112.50) --
	(240.50,116.23) --
	(245.86,130.94) --
	(251.21,168.51);
\definecolor{drawColor}{RGB}{231,41,138}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (203.04, 68.42) --
	(208.39, 63.98) --
	(213.74, 63.98) --
	(219.09, 63.98);
\definecolor{fillColor}{RGB}{117,112,179}

\path[fill=fillColor] (201.07,111.28) --
	(205.00,111.28) --
	(205.00,115.20) --
	(201.07,115.20) --
	cycle;

\path[fill=fillColor] (206.43,109.89) --
	(210.35,109.89) --
	(210.35,113.82) --
	(206.43,113.82) --
	cycle;

\path[fill=fillColor] (211.78,109.63) --
	(215.70,109.63) --
	(215.70,113.55) --
	(211.78,113.55) --
	cycle;

\path[fill=fillColor] (217.13,109.70) --
	(221.06,109.70) --
	(221.06,113.62) --
	(217.13,113.62) --
	cycle;

\path[fill=fillColor] (222.49,110.16) --
	(226.41,110.16) --
	(226.41,114.09) --
	(222.49,114.09) --
	cycle;

\path[fill=fillColor] (227.84,110.31) --
	(231.76,110.31) --
	(231.76,114.23) --
	(227.84,114.23) --
	cycle;

\path[fill=fillColor] (233.19,110.53) --
	(237.11,110.53) --
	(237.11,114.46) --
	(233.19,114.46) --
	cycle;

\path[fill=fillColor] (238.54,114.27) --
	(242.47,114.27) --
	(242.47,118.20) --
	(238.54,118.20) --
	cycle;

\path[fill=fillColor] (243.90,128.97) --
	(247.82,128.97) --
	(247.82,132.90) --
	(243.90,132.90) --
	cycle;

\path[fill=fillColor] (249.25,166.55) --
	(253.17,166.55) --
	(253.17,170.47) --
	(249.25,170.47) --
	cycle;
\definecolor{fillColor}{RGB}{217,95,2}

@@

\path[fill=fillColor] (203.04, 90.42) --
	(205.68, 85.84) --
	(200.39, 85.84) --
	cycle;

\path[fill=fillColor] (208.39, 90.41) --
	(211.03, 85.84) --
	(205.75, 85.84) --
	cycle;

\path[fill=fillColor] (213.74, 90.41) --
	(216.38, 85.84) --
	(211.10, 85.84) --
	cycle;

\path[fill=fillColor] (219.09, 90.41) --
	(221.74, 85.84) --
	(216.45, 85.84) --
	cycle;

\path[fill=fillColor] (224.45, 90.41) --
	(227.09, 85.84) --
	(221.80, 85.84) --
	cycle;

\path[fill=fillColor] (229.80, 90.41) --
	(232.44, 85.84) --
	(227.16, 85.84) --
	cycle;

\path[fill=fillColor] (235.15, 90.42) --
	(237.79, 85.84) --
	(232.51, 85.84) --
	cycle;

\path[fill=fillColor] (240.50, 90.49) --
	(243.15, 85.92) --
	(237.86, 85.92) --
	cycle;

\path[fill=fillColor] (245.86, 91.39) --
	(248.50, 86.82) --
	(243.21, 86.82) --
	cycle;

\path[fill=fillColor] (251.21,100.21) --
	(253.85, 95.64) --
	(248.57, 95.64) --
	cycle;

\path[fill=fillColor] (256.56,126.40) --
	(259.20,121.82) --
	(253.92,121.82) --
	cycle;

\path[fill=fillColor] (261.91,160.59) --
	(264.56,156.02) --
	(259.27,156.02) --
	cycle;

\path[fill=fillColor] (267.27,195.39) --
	(269.91,190.81) --
	(264.62,190.81) --
	cycle;

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (200.26, 68.42) -- (205.81, 68.42);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (203.04, 65.64) -- (203.04, 71.19);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (205.61, 63.98) -- (211.16, 63.98);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (208.39, 61.20) -- (208.39, 66.75);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (210.97, 63.98) -- (216.52, 63.98);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (213.74, 61.20) -- (213.74, 66.75);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (216.32, 63.98) -- (221.87, 63.98);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (219.09, 61.20) -- (219.09, 66.75);
\definecolor{fillColor}{RGB}{27,158,119}

@@

\path[fill=fillColor] (203.04, 87.62) circle (  1.96);

\path[fill=fillColor] (208.39, 87.61) circle (  1.96);

\path[fill=fillColor] (213.74, 87.61) circle (  1.96);

\path[fill=fillColor] (219.09, 87.61) circle (  1.96);

\path[fill=fillColor] (224.45, 87.61) circle (  1.96);

\path[fill=fillColor] (229.80, 87.61) circle (  1.96);

\path[fill=fillColor] (235.15, 87.62) circle (  1.96);

\path[fill=fillColor] (240.50, 87.69) circle (  1.96);

\path[fill=fillColor] (245.86, 88.58) circle (  1.96);

\path[fill=fillColor] (251.21, 97.29) circle (  1.96);

\path[fill=fillColor] (256.56,123.32) circle (  1.96);

\path[fill=fillColor] (261.91,157.55) circle (  1.96);

\path[fill=fillColor] (267.27,192.33) circle (  1.96);
\definecolor{drawColor}{gray}{0.70}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (192.33, 57.56) -- (192.33, 63.25);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (203.04, 57.56) -- (203.04, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (208.39, 57.56) -- (208.39, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (213.74, 57.56) -- (213.74, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (219.09, 57.56) -- (219.09, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (224.45, 57.56) -- (224.45, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (229.80, 57.56) -- (229.80, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (235.15, 57.56) -- (235.15, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (240.50, 57.56) -- (240.50, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (245.86, 57.56) -- (245.86, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (251.21, 57.56) -- (251.21, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (256.56, 57.56) -- (256.56, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (261.91, 57.56) -- (261.91, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (267.27, 57.56) -- (267.27, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (272.62, 57.56) -- (272.62, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (277.97, 57.56) -- (277.97, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (283.32, 57.56) -- (283.32, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (288.68, 57.56) -- (288.68, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (294.03, 57.56) -- (294.03, 63.25);

>>>>

% Created by tikzDevice version 0.12.6 on 2024-08-07 14:16:35
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 42.89, 57.56) --
	( 42.89,198.75);

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 81.85, 57.56) --
	( 81.85,198.75);

\path[draw=drawColor,line width= 0.2pt,line join=round] (120.82, 57.56) --
	(120.82,198.75);

\path[draw=drawColor,line width= 0.2pt,line join=round] (159.78, 57.56) --
	(159.78,198.75);

@@

\path[draw=drawColor,line width= 0.5pt,line join=round] ( 62.37, 57.56) --
	( 62.37,198.75);

\path[draw=drawColor,line width= 0.5pt,line join=round] (101.34, 57.56) --
	(101.34,198.75);

\path[draw=drawColor,line width= 0.5pt,line join=round] (140.30, 57.56) --
	(140.30,198.75);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.10,106.36) --
	( 45.67,106.36) --
	( 51.24,106.36) --
	( 56.80,106.36) --
	( 62.37,106.36) --
	( 67.94,106.37) --
	( 73.50,106.38) --
	( 79.07,106.42) --
	( 84.64,106.58) --
	( 90.20,107.23) --
	( 95.77,109.99) --
	(101.34,117.90);
\definecolor{drawColor}{RGB}{117,112,179}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 40.10,123.48) --
	( 45.67,112.22) --
	( 51.24,112.22) --
	( 56.80,112.42) --
	( 62.37,119.02) --
	( 67.94,162.96);
\definecolor{fillColor}{RGB}{27,158,119}

@@

\path[fill=fillColor] ( 45.67,106.36) circle (  1.96);

\path[fill=fillColor] ( 51.24,106.36) circle (  1.96);

\path[fill=fillColor] ( 56.80,106.36) circle (  1.96);

\path[fill=fillColor] ( 62.37,106.36) circle (  1.96);

\path[fill=fillColor] ( 67.94,106.37) circle (  1.96);

\path[fill=fillColor] ( 73.50,106.38) circle (  1.96);

\path[fill=fillColor] ( 79.07,106.42) circle (  1.96);

\path[fill=fillColor] ( 84.64,106.58) circle (  1.96);

\path[fill=fillColor] ( 90.20,107.23) circle (  1.96);

\path[fill=fillColor] ( 95.77,109.99) circle (  1.96);

\path[fill=fillColor] (101.34,117.90) circle (  1.96);
\definecolor{fillColor}{RGB}{117,112,179}

\path[fill=fillColor] ( 38.14,121.52) --
	( 42.06,121.52) --
	( 42.06,125.44) --
	( 38.14,125.44) --
	cycle;

\path[fill=fillColor] ( 43.71,110.26) --
	( 47.63,110.26) --
	( 47.63,114.18) --
	( 43.71,114.18) --
	cycle;

\path[fill=fillColor] ( 49.27,110.26) --
	( 53.20,110.26) --
	( 53.20,114.18) --
	( 49.27,114.18) --
	cycle;

\path[fill=fillColor] ( 54.84,110.46) --
	( 58.76,110.46) --
	( 58.76,114.38) --
	( 54.84,114.38) --
	cycle;

\path[fill=fillColor] ( 60.41,117.06) --
	( 64.33,117.06) --
	( 64.33,120.99) --
	( 60.41,120.99) --
	cycle;

\path[fill=fillColor] ( 65.97,161.00) --
	( 69.90,161.00) --
	( 69.90,164.92) --
	( 65.97,164.92) --
	cycle;
\definecolor{drawColor}{gray}{0.70}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 34.54, 57.56) -- ( 34.54, 63.25);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 45.67, 57.56) -- ( 45.67, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 51.24, 57.56) -- ( 51.24, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 56.80, 57.56) -- ( 56.80, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 62.37, 57.56) -- ( 62.37, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 67.94, 57.56) -- ( 67.94, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 73.50, 57.56) -- ( 73.50, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 79.07, 57.56) -- ( 79.07, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 84.64, 57.56) -- ( 84.64, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 90.20, 57.56) -- ( 90.20, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 95.77, 57.56) -- ( 95.77, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (101.34, 57.56) -- (101.34, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (106.90, 57.56) -- (106.90, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (112.47, 57.56) -- (112.47, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (118.04, 57.56) -- (118.04, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (123.60, 57.56) -- (123.60, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (129.17, 57.56) -- (129.17, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (134.74, 57.56) -- (134.74, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (140.30, 57.56) -- (140.30, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (145.87, 57.56) -- (145.87, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (151.44, 57.56) -- (151.44, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (157.00, 57.56) -- (157.00, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (162.57, 57.56) -- (162.57, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (168.13, 57.56) -- (168.13, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (173.70, 57.56) -- (173.70, 63.25);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (184.83, 57.56) -- (184.83, 63.25);

@@

\path[draw=drawColor,line width= 0.2pt,line join=round] (200.47, 57.56) --
	(200.47,198.75);

\path[draw=drawColor,line width= 0.2pt,line join=round] (239.43, 57.56) --
	(239.43,198.75);

\path[draw=drawColor,line width= 0.2pt,line join=round] (278.40, 57.56) --
	(278.40,198.75);

\path[draw=drawColor,line width= 0.2pt,line join=round] (317.37, 57.56) --
	(317.37,198.75);

@@

\path[draw=drawColor,line width= 0.5pt,line join=round] (219.95, 57.56) --
	(219.95,198.75);

\path[draw=drawColor,line width= 0.5pt,line join=round] (258.92, 57.56) --
	(258.92,198.75);

\path[draw=drawColor,line width= 0.5pt,line join=round] (297.88, 57.56) --
	(297.88,198.75);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (197.68, 87.62) --
	(203.25, 87.61) --
	(208.82, 87.61) --
	(214.38, 87.61) --
	(219.95, 87.61) --
	(225.52, 87.61) --
	(231.08, 87.62) --
	(236.65, 87.69) --
	(242.22, 88.58) --
	(247.78, 97.29) --
	(253.35,123.32) --
	(258.92,157.55) --
	(264.48,192.33);
\definecolor{drawColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (197.68, 87.37) --
	(203.25, 87.36) --
	(208.82, 87.36) --
	(214.38, 87.36) --
	(219.95, 87.36) --
	(225.52, 87.36) --
	(231.08, 87.37) --
	(236.65, 87.44) --
	(242.22, 88.34) --
	(247.78, 97.16) --
	(253.35,123.35) --
	(258.92,157.54) --
	(264.48,192.33);
\definecolor{drawColor}{RGB}{117,112,179}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (197.68,113.24) --
	(203.25,111.85) --
	(208.82,111.59) --
	(214.38,111.66) --
	(219.95,112.12) --
	(225.52,112.27) --
	(231.08,112.50) --
	(236.65,116.23) --
	(242.22,130.94) --
	(247.78,168.51);
\definecolor{drawColor}{RGB}{231,41,138}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (197.68, 68.42) --
	(203.25, 63.98) --
	(208.82, 63.98) --
	(214.38, 63.98);
\definecolor{fillColor}{RGB}{117,112,179}

\path[fill=fillColor] (195.72,111.28) --
	(199.65,111.28) --
	(199.65,115.20) --
	(195.72,115.20) --
	cycle;

\path[fill=fillColor] (201.29,109.89) --
	(205.21,109.89) --
	(205.21,113.82) --
	(201.29,113.82) --
	cycle;

\path[fill=fillColor] (206.86,109.63) --
	(210.78,109.63) --
	(210.78,113.55) --
	(206.86,113.55) --
	cycle;

\path[fill=fillColor] (212.42,109.70) --
	(216.35,109.70) --
	(216.35,113.62) --
	(212.42,113.62) --
	cycle;

\path[fill=fillColor] (217.99,110.16) --
	(221.91,110.16) --
	(221.91,114.09) --
	(217.99,114.09) --
	cycle;

\path[fill=fillColor] (223.56,110.31) --
	(227.48,110.31) --
	(227.48,114.23) --
	(223.56,114.23) --
	cycle;

\path[fill=fillColor] (229.12,110.53) --
	(233.05,110.53) --
	(233.05,114.46) --
	(229.12,114.46) --
	cycle;

\path[fill=fillColor] (234.69,114.27) --
	(238.61,114.27) --
	(238.61,118.20) --
	(234.69,118.20) --
	cycle;

\path[fill=fillColor] (240.26,128.97) --
	(244.18,128.97) --
	(244.18,132.90) --
	(240.26,132.90) --
	cycle;

\path[fill=fillColor] (245.82,166.55) --
	(249.75,166.55) --
	(249.75,170.47) --
	(245.82,170.47) --
	cycle;
\definecolor{fillColor}{RGB}{217,95,2}

@@

\path[fill=fillColor] (203.25, 90.41) --
	(205.89, 85.84) --
	(200.61, 85.84) --
	cycle;

\path[fill=fillColor] (208.82, 90.41) --
	(211.46, 85.84) --
	(206.18, 85.84) --
	cycle;

\path[fill=fillColor] (214.38, 90.41) --
	(217.03, 85.84) --
	(211.74, 85.84) --
	cycle;

\path[fill=fillColor] (219.95, 90.41) --
	(222.59, 85.84) --
	(217.31, 85.84) --
	cycle;

\path[fill=fillColor] (225.52, 90.41) --
	(228.16, 85.84) --
	(222.88, 85.84) --
	cycle;

\path[fill=fillColor] (231.08, 90.42) --
	(233.73, 85.84) --
	(228.44, 85.84) --
	cycle;

\path[fill=fillColor] (236.65, 90.49) --
	(239.29, 85.92) --
	(234.01, 85.92) --
	cycle;

\path[fill=fillColor] (242.22, 91.39) --
	(244.86, 86.82) --
	(239.57, 86.82) --
	cycle;

\path[fill=fillColor] (247.78,100.21) --
	(250.43, 95.64) --
	(245.14, 95.64) --
	cycle;

\path[fill=fillColor] (253.35,126.40) --
	(255.99,121.82) --
	(250.71,121.82) --
	cycle;

\path[fill=fillColor] (258.92,160.59) --
	(261.56,156.02) --
	(256.27,156.02) --
	cycle;

\path[fill=fillColor] (264.48,195.39) --
	(267.13,190.81) --
	(261.84,190.81) --
	cycle;

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.91, 68.42) -- (200.46, 68.42);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.68, 65.64) -- (197.68, 71.19);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (200.48, 63.98) -- (206.03, 63.98);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (203.25, 61.20) -- (203.25, 66.75);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (206.04, 63.98) -- (211.59, 63.98);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (208.82, 61.20) -- (208.82, 66.75);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (211.61, 63.98) -- (217.16, 63.98);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (214.38, 61.20) -- (214.38, 66.75);
\definecolor{fillColor}{RGB}{27,158,119}

@@

\path[fill=fillColor] (203.25, 87.61) circle (  1.96);

\path[fill=fillColor] (208.82, 87.61) circle (  1.96);

\path[fill=fillColor] (214.38, 87.61) circle (  1.96);

\path[fill=fillColor] (219.95, 87.61) circle (  1.96);

\path[fill=fillColor] (225.52, 87.61) circle (  1.96);

\path[fill=fillColor] (231.08, 87.62) circle (  1.96);

\path[fill=fillColor] (236.65, 87.69) circle (  1.96);

\path[fill=fillColor] (242.22, 88.58) circle (  1.96);

\path[fill=fillColor] (247.78, 97.29) circle (  1.96);

\path[fill=fillColor] (253.35,123.32) circle (  1.96);

\path[fill=fillColor] (258.92,157.55) circle (  1.96);

\path[fill=fillColor] (264.48,192.33) circle (  1.96);
\definecolor{drawColor}{gray}{0.70}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (192.12, 57.56) -- (192.12, 63.25);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (203.25, 57.56) -- (203.25, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (208.82, 57.56) -- (208.82, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (214.38, 57.56) -- (214.38, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (219.95, 57.56) -- (219.95, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (225.52, 57.56) -- (225.52, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (231.08, 57.56) -- (231.08, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (236.65, 57.56) -- (236.65, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (242.22, 57.56) -- (242.22, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (247.78, 57.56) -- (247.78, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (253.35, 57.56) -- (253.35, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (258.92, 57.56) -- (258.92, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (264.48, 57.56) -- (264.48, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (270.05, 57.56) -- (270.05, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (275.62, 57.56) -- (275.62, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (281.18, 57.56) -- (281.18, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (286.75, 57.56) -- (286.75, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (292.32, 57.56) -- (292.32, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (297.88, 57.56) -- (297.88, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (303.45, 57.56) -- (303.45, 63.25);
